\section*{Abstract}
Communication intensive applications in data center hosts with multi-core CPU and high-speed networking hardware often put considerable stress on the socket system.
%Communication intensive applications on modern computers with multi-core CPU and high-speed networking hardware 
%often put considerable stress on traditional socket implementation. 
Linux socket is implemented in the kernel space with shared data structures that needs concurrency protection, which incurs significant overhead.
%This design incurs significant kernel crossing and locking overhead.
Recent user-space sockets often do not support intra-host communication among containers and applications, or have limitations on compatibility, isolation and multi-thread scalability.

In this paper, we describe \sys{}, a high performance socket system that is fully compatible with Linux socket and can be used as a drop-in replacement with no modification to applications.
\sys{} is implemented in user space to avoid kernel crossing cost.
It achieves multi-thread scalability by considering threads as a shared-nothing message passing distributed system.
To improve memory locality, we multiplex all connections and event notifications between a pair of threads via one queue.
\sys{} uses a high performance shared memory lockless queue for intra-host communication.
For inter-host communication, it takes advantage of modern RDMA hardware, but can also transparently communicate with regular TCP/IP endpoints.
Together with carefully designed zero-copy mechanism and cooperative multitasking, it removes many overheads of existing socket systems.
Experiment shows that \sys achieves 4 to 24x better message throughput, 10 to 60x better latency, and over 40x connection setup throughput compared with Linux socket.


\iffalse
\textbf{Title Candidates:}

%IPC-Direct: Fast and Compatible Inter-Process Communication in User Space

IPC-Direct: A Fast and Linux-Compatible Architecture for Inter-Process Communication

%IPC-Direct: Rethinking Processes as a Distributed System

%IPC-Direct: Rethinking Cores as a Distributed System

IPC-Direct: Accelerating Linux Sockets by Rethinking Processes as a Distributed System

SocksDirect: Push-Button Acceleration of Linux Socket

Rethinking Processes as a Distributed System: A Fast and Compatible Sockets Design

SocksDirect: High Performance Drop-in Replacement for Linux Socket

SocksDirect: High Performance Drop-in Replacement for Linux Socket in Multi-core RDMA Systems

High Performance Drop-in Replacement for Linux Socket: A Distributed Approach

High Performance Drop-in Replacement for Linux Socket: A Distributed Systems Perspective

High Performance Drop-in Replacement for Linux Socket from Distributed Systems Perspective

High Performance Drop-in Replacement for Linux Socket: A Distributed Library Operating System

\textit{IPC-Direct: A High Performance Operating System Architecture with Linux Compatibility}

\textit{SocksDirect: A High Performance and Linux Compatible Library Operating System}

\textbf{Key points that must be mentioned in the title:}

\begin{itemize}
	\item Fast / High Performance
	\item Compatible / Drop-in Replacement
\end{itemize}

\textbf{Key points that may be mentioned in the title:}

\begin{itemize}
	\item Sockets / Linux Socket / Inter-Process Communication
	\item Operating System / Architecture
	\item User Space / Library
	\item Distributed / Decentralized
	\item Multi-core / RDMA
	\item System name: IPC-Direct / SocksDirect
\end{itemize}
\fi